Quality measure notes

### 2021-08-08 StateOfPractice/Ao-Report/13Methods.tex
MI report - update ch 3

\item Finally, we removed \textit{Open Dicom Viewer} from the list because it had not received any updates for a long time.
\end{enumerate}

After that, there were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply this filter since packages were already below 30. However, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub. Furthermore, 27 packages had the latest updates after the year 2018, and 23 after 2020.

>>>>

\item Finally, we removed \textit{Open Dicom Viewer} from the list because it had not received any updates for a long time (since 2011). After that, only \textit{MatrixUser} and \textit{AMIDE} were considered as ``dead". However, both of them had much more recent updates (after 2017) than \textit{Open Dicom Viewer}.
\end{enumerate}

There were 29 software products left on the list. We still preferred projects using git and GitHub and being updated recently, but did not apply this filter since packages were already below 30. Even without this filter, 27 out of the 29 software packages on the final list used git, and 24 chose GitHub.
